\newpage

\begin{center}
{\bfseries \Large Lisa Smith}
\end{center}

\begin{center}
\begin{tabular}{p{0.95\linewidth}}
Department of Electrical and Computer Engineering \\
Dwight Look College of Engineering
\hfill Phone: 972-922-8758 \\
Texas A\&M University
\hfill \texttt{lisa.smith75056@tamu.edu} \\
College Station, TX 77840
\end{tabular}
\end{center}

\textbf{Keywords:} RF/microwave systems, antenna design, reconfigurable antennas, adaptive structures, measurement and testing.

\subsection*{Professional Preparation}

\begin{center}
\begin{tabular}{p{0.95\linewidth}}
\textbf{Bachelor of Science}, Electrical Engineering \hfill Senior Student \\
Physics (minor) \& Mathematics (minor) \\
Department of Electrical and Computer Engineering \hfill GPA: 3.434 \\
Texas A\&M University
\end{tabular}
\end{center}

\subsection*{Appointments}

\begin{center}
\begin{tabular}{p{0.95\linewidth}}
\textbf{Research Assistant} \hfill 2014--2015 \\
Electromagnetics and Microwave Laboratory \\
Department of Electrical and Computer Engineering \\
Texas A\&M University
\end{tabular}
\end{center}

\subsection*{Publications and Projects}

\begin{enumerate} \partopsep0pt \topsep0pt \parsep0pt \itemsep0pt
\item Project: Liquid Metal Reconfigurable Antennas Embedded in Structural Composites.
\newblock{Huff Research Group, Electromagnetics and Microwave Laboratory, 2012--2016.}

\item Project: Enabling Large-Scale Water Distribution, Management, and Monitoring through the Internet of Everything.
\newblock{Aggie Engineering Challenge, 2015--2016.}

\item Project: A Bio-Inspired Autonomous Underwater Vehicle for Infrastructure Monitoring and Sub-Sea Exploration, and Search and Rescue Operations.
\newblock{Aggie Engineering Challenge, 2014--2015.}
\end{enumerate}

\textbf{Software/Prototyping:} ANSYS HFSS, Matlab, PCB design, 3D design (CAD), 3D printing.

\textbf{Selected Course Topics:} Applied electromagnetic theory, microwave circuits and systems, RF \& microwave wireless, antenna engineering, microelectronic fabrication.

