\newpage

\begin{center}
{\bfseries \Large Travis Taghavi}
\end{center}

\begin{center}
\begin{tabular}{p{0.95\linewidth}}
Department of Electrical and Computer Engineering
\hfill Phone: 713-825-2057 \\
Dwight Look College of Engineering
\hfill Fax: 979-862-4630 \\
Texas A\&M University
\hfill \texttt{travistag@tamu.edu} \\
College Station, TX 77843-3128
\hfill \texttt{travistag.github.io}
\end{tabular}
\end{center}

\textbf{Keywords:} Wireless networks, sensing modules, complex systems, statistical signal processing, inference, machine learning, RF/microwave systems, autonomous vehicles.

\subsection*{Professional Preparation}

\begin{center}
\begin{tabular}{p{0.95\linewidth}}
\textbf{Master of Science}, Computer Engineering \hfill Candidate \\
Department of Electrical and Computer Engineering \hfill Current GPA: 4.0 \\
Texas A\&M University \\[2mm]
\textbf{Bachelor of Science}, Computer Engineering (major) \& Mathematics (minor) \hfill 2014 \\
{\em magna cum laude}\\
Department of Electrical and Computer Engineering \hfill GPA: 3.735\\
Texas A\&M University
\end{tabular}
\end{center}

\subsection*{Appointments}

\begin{center}
\begin{tabular}{p{0.95\linewidth}}
\textbf{Research Assistant} \hfill 2015--present \\
Department of Electrical and Computer Engineering \\
Texas A\&M University \\[4pt]
\textbf{Hardware Design Engineering} \hfill 2014--2015 \\
Hewlett-Packard \\
Austin, TX
\end{tabular}
\end{center}

\subsection*{Publications and Projects}

\begin{enumerate} \partopsep0pt \topsep0pt \parsep0pt \itemsep0pt

\item T.~Taghavi, J.-F. Chamberland, and G.~H. Huff.
\newblock \href{http://dx.doi.org/10.1109/USNC-URSI-NRSM.2014.6927995}{Antenna design for graph inference: Striking a balance between quality and quantity}.
\newblock {\em National Radio Science Meeting, Boulder, CO}, 2014.

\item D.~Tunon, T.~Taghavi, J.-F. Chamberland, and G.~H. Huff.
\newblock \href{http://dx.doi.org/10.1109/USNC-URSI-NRSM.2014.6928007}{On the design and analysis of antenna patterns for localization with smart devices}.
\newblock {\em National Radio Science Meeting, Boulder, CO}, 2014.

\item D.~Tunon, T.~Taghavi, J.-F. Chamberland, and G.~H. Huff.
\newblock \href{http://dx.doi.org/10.1109/GlobalSIP.2013.6736829}{Localization of a single source with orientation-aware smart devices}.
\newblock {\em Global Conference on Signal and Information Processing, Austin, TX}, 2013.

\item T.~Taghavi.
\newblock \href{http://hdl.handle.net/1969.1/152045}{Device Association Through Passive Wi-Fi Monitoring}.
\newblock {\em Honors and Undergraduate Research}, Texas A\&M University, 2014.

\item T.~Taghavi, J.-F. Chamberland, and G.~H. Huff.
\newblock Leveraging Reconfigurable Antennas and Machine Learning in Inference Tasks Based on Wi-Fi Metadata.
\newblock {\em National Radio Science Meeting, Boulder, CO}, 2016
\end{enumerate}

\textbf{Software/Prototyping:} C/C++, Java, Python, SQLite,
Android development, microcontrollers,
version control system (e.g. Git), Doxygen, Matlab,
3D design (CAD), 3D printing, PCB design.

\textbf{Selected Course Topics:} Probability and random processes, vector space methods, data acquisition, embedded systems, linear control, artificial intelligence, algorithms.

